\textsf{Are large language models superhuman chemists?}

### 2024-10-19 src/tex/sections/manually_sources_table.tex
[showyourwork]
fix overleaf sync messup
first additions

>>>>

Spectroscopy & Based on exams at the University of Hamburg, Germany && \variable{output/question_count_per_dir/json_file_counts_spectroscopy.txt} \\
Solid state chemistry & Based on lectures published on the YouTube channels "Material Universe", "Advanced Cyberinfrastructure Training at RPI", "Phase Diagrams in Materials Science and Engineering" && 9\\
                    & Based on the website \href{Wayback Machine}{https://archive.org/details/AshcroftSolidState/page/128/mode/2up} && 4\\
                    & Based on the \href{https://ocw.mit.edu/courses/3-091sc-introduction-to-solid-state-chemistry-fall-2010/pages/organic-materials/29-polymers-synthesis-properties-applications/}{lecture notes} published by the Massachusetts Institute of Technology (MIT) && 4\\
Technical chemistry & Based on notes from lectures at school at the University of Oviedo && 12\\
                    & Based on the chemical engineering textbook from Octave Levenspiel && 8\\
                    & Based on a lecture at the IIT Kharagpur, India && 1\\
Hybridization questions &  Based on exams at the Ecole Polytechnique Federale de Lausanne && 9\\
Biochemistry & Based on exams at the FSU Jena, Germany && 7\\
Physical Chemistry & Based on a textbook & 6\\
